---
title: "DSC 200 Lab Project -Term 2232"
date: "`r Sys.Date()`"
output: github_document
---

**Student Name:<Al_Shaya_Almasar>**

**Student ID:<insert 2210002236>**


**Deadline:** 23:59 on Sunday, 19 May 2024

**Total Points:** 20


## Loading Packages

```{r load-packages, message = FALSE}

library(tidyverse)
library(openintro)
library(ggrepel)
```


## Tasks

`1. (2 points)
```{r}
 seattlepets %>%
distinct (species)
```
Write your narrative here




`2. (2 points)

```{r}
seattlepets %>%
  ncol()
```
Write your narrative below



`3. (2 points)
```{r}
seattlepets %>%
select (species) %>%
  count(species , sort = TRUE)
```
Write your narrative here


`4. (2 points)
```{r}
seattlepets %>% 
  select(animal_name) %>%
  count(animal_name , sort = TRUE)

```
Write your narrative here


`5. (2 points)
```{r}
seattlepets %>%
filter(species == "Pig") %>%
  arrange(animal_name)
```
Write your narrative here




`6. (2 points)
```{r}
seattlepets %>%
  filter(species == "Goat") %>%
  select(animal_name , primary_breed) %>%
  arrange(animal_name)
```
Write your narrative here





`7. (2 points)
```{r}
seattlepets %>%
  mutate(pet = animal_name , species) %>%
  select(license_number , pet) %>%
  arrange(pet)
```
Write your narrative here



`8. (2 points)
```{r}
ggplot(seattlepets,aes(x=species))+
  geom_bar();
```
Write your narrative here




`9. (2 points)
```{r}
top_10_names <- seattlepets %>% 
filter(animal_name %in% c( "Lucy"  , "Charlie" , "Luna" , "Bella" , "Max"    , 
                           "Daisy" , "Molly"   , "Jack" , "Lily"  , "Stella" ))
top_10_names
```
`a.	What does the above code chunk do?
The code performs the following actions:

1. **Selecting Popular Pet Names:**
   - It filters the `animal_name` column in the `seattlepets` data frame to include only rows where the pet's name is one of the specified names: ("Lucy", "Charlie", "Luna", "Bella", "Max", "Daisy", "Molly", "Jack", "Lily", "Stella").

2. **Creating a New Data Frame:**
   - The filtered result is stored in a new data frame called `top_10_names`.

In summary, the code filters the `seattlepets` data frame to include only the rows with the ten specified pet names and stores this filtered data in `top_10_names`.


`b. Plot the counts of the pet names (animal_name) in top_10_names
```{r}
seattlepets %>%
  filter(animal_name %in% c( "Lucy"  , "Charlie" , "Luna" , "Bella" , "Max"    , 
                           "Daisy" , "Molly"   , "Jack" , "Lily"  , "Stella" )) %>%
  ggplot(aes(animal_name , 
             fill = species)) + 
  geom_bar()
```


`10.  (2 points)

`The below code plots the proportion of dogs with a given name versus the proportion of cats with the same name. The 20 most common cat and dog names are displayed. The diagonal line on the plot is the x = y line; if a name appeared on this line, the name’s popularity would be exactly the same for dogs and cats.

```{r eval = TRUE, echo = FALSE, fig.fullwidth = TRUE}
# data prep
name_props <- seattlepets %>% 
  filter(
    !is.na(animal_name),
    species %in% c("Dog", "Cat")
    ) %>%
  group_by(species) %>% 
  count(animal_name, sort = TRUE) %>%
  mutate(prop = n / sum(n))
    
cat_name_props <- name_props %>%
  filter(species == "Cat") %>%
  rename(cat_prop = prop) %>%
  slice(1:30)

dog_name_props <- name_props %>%
  filter(species == "Dog") %>%
  rename(dog_prop = prop) %>%
  slice(1:30)
    
comb_name_props <- inner_join(cat_name_props, dog_name_props, 
                              by = "animal_name") %>%
  ungroup() %>%
  select(animal_name, cat_prop, dog_prop)
    
# create viz
ggplot(comb_name_props, aes(x = cat_prop, y = dog_prop)) +
  geom_abline(intercept = 0, 
              color = COL["lgray","full"], 
              alpha = 0.8, 
              size = 1.5) +
  geom_text_repel(aes(label = animal_name), 
                  segment.color = COL["gray","full"], 
                  seed = 291252, max.iter = 10000) +
  geom_point(color = COL["blue","full"], alpha = 0.8) +
  theme_minimal() +
  labs(x = "Proportion of cats", y = "Proportion of dogs") +
  xlim(0.002, 0.01) +
  ylim(0.002, 0.01) +
  ggimage::geom_emoji(
      image = "1f436", aes(x = 0.003, y = 0.009), size = 0.1
      ) +
  ggimage::geom_emoji(
      image = "1f431", aes(x = 0.009, y = 0.003), size = 0.1
      )
```

`What names are more common for cats than dogs? The ones above the line or the ones below the line?

`Answer here..................
 **The names listed below the line are more common for cats than for dogs.**


`Is the relationship between the two variables (proportion of cats with a given name and proportion of dogs with a given name) positive or negative? What does this mean in context of the data?

`Answer here .............
**The relationship between the two variables is positive, meaning that as the proportion of cats with a given name increases, the proportion of dogs with the same name also tends to increase.**
